### 2013-08-15 Tex/chapters/results.tex
Bild, warum die Querverbindungen beim GG entstehen

        \caption[Critical Temperature Normalized by Degree of the Graph]
        {
            Top: Degree \(K\) of graph over different
            disorder parameters \(\sigma\) for
            \subref{sfig:deg:RNG} the RNG and
            \subref{sfig:deg:GG} the GG.\\
            Bottom: Critical temperatures normalized by degree over different
            disorder parameters for
            \subref{sfig:Tc_norm_deg:RNG} the RNG and
            \subref{sfig:Tc_norm_deg:GG} the GG.
        }
        \label{fig:Tc_deg}
    \end{figure}\\
    To understand the jump of \(T_c\), it seems to be necessary to
    understand the jump of \(K\), which is easily explained
    by the definition of the GG and its aftereffects for
    the transition from \(\sigma = 0\). Visible in Fig.\ \ref{fig:GG_sigma}\subref{sfig:GG_sigma:0.00}\subref{sfig:GG_sigma:0.01}
    a small change of \(\sigma\) causes many new edges to arise\footnote{See also \url{http://www.youtube.com/watch?v=PcVZ2pG11GI} for an animation.}.
    To fully understand this, take four nodes forming a square. The edge
    across does not exist, because the other two nodes are on the edge
    of the lune. Moving one node slightly into the square, causes the lune
    to get smaller, hence no other nodes are inside or on the edge of
    the lune anymore and the edge appears.\\
    Further the increase of \(T_c\) on the GG can be made plausible.
    %~ Though it is not removed by the normalization, it is reduced.
    Also the maximum of the \(K\) is at the same \(\sigma\), as the maximum
    of \(T_c\). So while displacing the nodes, there arise more edges
    than edges are vanishing until \(\sigma \approx 0.15\) is reached.
    Then more edges disappear, than appear at further displacement. This
    is not an obvious effect, but can be seen in Fig.\ \ref{fig:GG_sigma}\subref{sfig:GG_sigma:0.09}\subref{sfig:GG_sigma:0.15}\subref{sfig:GG_sigma:0.21}
    \begin{figure}[htbp]
        \subfigure[][$\sigma = 0.00$]
        {
            \label{sfig:GG_sigma:0.00}
            \includegraphics[width=0.30\textwidth]{images/GG/sigma_e0}
        }
        \subfigure[][$\sigma = 0.01$]
        {
            \label{sfig:GG_sigma:0.01}
            \includegraphics[width=0.30\textwidth]{images/GG/sigma_g0}
        }

        \subfigure[][$\sigma = 0.09$]
        {
            \label{sfig:GG_sigma:0.09}
            \includegraphics[width=0.30\textwidth]{images/GG/out009}
        }
        \subfigure[][$\sigma = 0.15$]
        {
            \label{sfig:GG_sigma:0.15}
            \includegraphics[width=0.30\textwidth]{images/GG/out015}Bild: parallel tmepering
Bild: cross edge GG
Bildunterschriften ausführlicher
        }
        \subfigure[][$\sigma = 0.21$]
        {
            \label{sfig:GG_sigma:0.21}
            \includegraphics[width=0.30\textwidth]{images/GG/out021}
        }

>>>>

        \caption[Critical Temperature Normalized by Degree of the Graph]
        {
            Top: Degree \(K\) of graph over different
            disorder parameters \(\sigma\) for
            \subref{sfig:deg:RNG} the RNG and
            \subref{sfig:deg:GG} the GG.\\
            Bottom: Critical temperatures normalized by degree over different
            disorder parameters for
            \subref{sfig:Tc_norm_deg:RNG} the RNG and
            \subref{sfig:Tc_norm_deg:GG} the GG.
        }
        \label{fig:Tc_deg}
    \end{figure}\\
    To understand the jump of \(T_c\), it seems to be necessary to
    understand the jump of \(K\), which is easily explained
    by the definition of the GG and its aftereffects for
    the transition from \(\sigma = 0\). Visible in Fig.\ \ref{fig:GG_sigma}\subref{sfig:GG_sigma:0.00}\subref{sfig:GG_sigma:0.01}
    a small change of \(\sigma\) causes many new edges to arise\footnote{See also \url{http://www.youtube.com/watch?v=PcVZ2pG11GI} for an animation.}.
    To fully understand this, take four nodes forming a square. The edge
    across does not exist, because the other two nodes are on the edge
    of the lune. Moving one node slightly into the square, causes the lune
    to get smaller, hence no other nodes are inside or on the edge of
    the lune anymore and the edge appears. This process is sketched in
    Fig.\ \ref{fig:GGEdge}
    \begin{figure}[htbp]
        \centering
        \subfigure[Definition of the Lunes][]{
            \label{sfig:GGEdge:before}
            \input{images/GGEdgeBefore}
        }
        \subfigure[RNG example][]{
            \label{sfig:GGEdge:after}
            \input{images/GGEdgeAfter}
        }
        \caption[Sketch why Many New Edges Arise at the Transition from $\sigma = 0$ to $\sigma > 0$]
        {
            \subref{sfig:GGEdge:before} The edge across does not exist,
            because the other two nodes are on the edge of the lune.
            \subref{sfig:GGEdge:after} Moving one node slightly into the
            square, causes the lune to get smaller, hence no other nodes
            are inside or on the edge of the lune anymore and the edge
            appears.
        }
        \label{fig:GGEdge}
    \end{figure}\\
    Further the increase of \(T_c\) on the GG can be made plausible.
    %~ Though it is not removed by the normalization, it is reduced.
    Also the maximum of the \(K\) is at the same \(\sigma\), as the maximum
    of \(T_c\). So while displacing the nodes, there arise more edges
    than edges are vanishing until \(\sigma \approx 0.15\) is reached.
    Then more edges disappear, than appear at further displacement. This
    is not an obvious effect, but can be seen in Fig.\ \ref{fig:GG_sigma}\subref{sfig:GG_sigma:0.09}\subref{sfig:GG_sigma:0.15}\subref{sfig:GG_sigma:0.21}
    \begin{figure}[htbp]
        \subfigure[][$\sigma = 0.00$]
        {
            \label{sfig:GG_sigma:0.00}
            \includegraphics[width=0.30\textwidth]{images/GG/sigma_e0}
        }
        \subfigure[][$\sigma = 0.01$]
        {
            \label{sfig:GG_sigma:0.01}
            \includegraphics[width=0.30\textwidth]{images/GG/sigma_g0}
        }

        \subfigure[][$\sigma = 0.09$]
        {
            \label{sfig:GG_sigma:0.09}
            \includegraphics[width=0.30\textwidth]{images/GG/out009}
        }
        \subfigure[][$\sigma = 0.15$]
        {
            \label{sfig:GG_sigma:0.15}
            \includegraphics[width=0.30\textwidth]{images/GG/out015}
        }
        \subfigure[][$\sigma = 0.21$]
        {
            \label{sfig:GG_sigma:0.21}
            \includegraphics[width=0.30\textwidth]{images/GG/out021}
        }
